Hypertension statistics for US adults: an open-source web application for analysis and visualization of US NHANES data

### 2022-11-11 paper/manuscript.Rmd
LC comment;
Note that the application can give various formats. We should be
specific about the formats available but there arent enough words in the
Methods section to list them. I will open an issue to specify file types
in the readme.
LC comment; calibration
noting that the calibration occurs in specific groups, consistent
with prior publications.

A full summary of this application’s features and associated tutorials are available online.[@rpack_cardioStatsUSA] Briefly, users can select NHANES cycles from 1999-2000 to 2017-2020 to be analyzed. Estimates are weighted to represent the non-institutionalized US population and users may incorporate age-adjustment through direct standardization. Users can restrict analyses to subsets of participants (e.g., participants who self-reported taking antihypertensive medication). When population count estimates are requested, survey weights are calibrated to account for missing information on SBP, DBP or self-reported antihypertensive medication use. The results can be presented in tables or figures and for the overall population or in subgroups. All tables and figures created with the web application can be downloaded and saved. Following CDC recommendations, unreliable statistical estimates are automatically suppressed.[@parker2017national] To increase precision and reliability of estimates, contiguous NHANES cycles can be combined.[@nhanes_tutorial_weights]

>>>>

A full summary of this application’s features and associated tutorials are available online.[@rpack_cardioStatsUSA] Briefly, users can select NHANES cycles from 1999-2000 to 2017-2020 to be analyzed. Estimates are weighted to represent the non-institutionalized US population and users may incorporate age-adjustment through direct standardization. Users can restrict analyses to subsets of participants (e.g., participants who self-reported taking antihypertensive medication). When population count estimates are requested, survey weights are calibrated within race, sex, and age groups to account for missing information on SBP, DBP or self-reported antihypertensive medication use. The results can be presented in tables or figures and for the overall population or in subgroups. All tables and figures created with the web application can be downloaded and saved in standard formats. Following CDC recommendations, unreliable statistical estimates are automatically suppressed.[@parker2017national] To increase precision and reliability of estimates, contiguous NHANES cycles can be combined.[@nhanes_tutorial_weights]
